\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-10-14 document/XSGRB_sample.tex
Notes on individual bursts

@@

%	\begin{figure}
%		%\vspace{11pc}   
%		%\includegraphics[width=10cm]{060218/6273fig1.ps}
%		\centerline{\includegraphics[width=8cm]{Resolution/resolution_paper.eps}}
%		\caption{Green datapoints show the FWHM (km/s) of Gaussian fits to unresolved telluric absorption lines in the VIS spectra, as a function of the FWHM of a Gaussian fit onto the trace in spatial direction at  792 nm. The lower horizontal axis is in units pixels, the top axis in arc seconds. The red datapoints show a subsample of NIR spectra.
%			The grey line shows a linear fit to the VIS datapoints. }
%		\label{fig:res}
%	\end{figure}

@@

@@

>>>>

	In cases where multiple traces are visible in the slit, additional components
	for the profile are used in the optimal extraction. The additional components
	share the PSF parameters and in cases where the additional component is an
	extended object, the fits have been inspected to ensure that the additional
	component does now skew the fit towards a broader PSF. The additional
	components are not used for the weights.

@@

	\begin{figure}
		\centerline{\includegraphics[width=8cm]{figures/resolution_paper.eps}}
		\caption{Green datapoints show the FWHM (km/s) of Gaussian fits to unresolved telluric absorption lines in the VIS spectra, as a function of the FWHM of a Gaussian fit onto the trace in spatial direction at  792 nm. The lower horizontal axis is in units pixels, the top axis in arc seconds. The red datapoints show a subsample of NIR spectra.
			The grey line shows a linear fit to the VIS datapoints. }
		\label{fig:res}
	\end{figure}

@@

	\subsection{GRB120224A (z = 1.10 NEW!!!)}
	The data presented here has formed the basis of GCN \#
	12991\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/12991.gcn3}}, and has also
	been published in \citet{Kruhler2015}. Starting 19.8 hours after the GRB
	trigger, a total exposure time of 2.4 ks reveals a faint continuum, starting at
	$\sim$ 7000 \AA~and extending all the way through 25000 \AA. We detect a $\sim
	2 \sigma$ emission line which, if interpreted as \ha, gives $z = 1.10$,
	supporting the redshift reported by \citet{Kruhler2015}.

	\subsection{GRB120311 (z = 0.350 NEW!!!)}
	The data presented here has formed the basis of GCN \#
	12991\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/12991.gcn3}}, but is not
	published otherwise. Starting just before twilight, 3.65 hours after the burst,
	a faint afterglow continuum is detected at all wavelengths. Due to the
	faintness of the afterglow, no absorption features are discernible superposed
	on the continuum. Displaced from the afterglow continuum by 1\farc4, emission
	lines belonging to \hb, \oiii~and \ha~are detected at $z = 0.350$. The line
	belonging to \ha~shows some extended emission toward the afterglow continuum.
	The angular distance between the two sources correspond to a projected distance
	in the host plane of 6 kpc, posing a potential problem for the host redshift,
	unless the GRB ocurred in a merging system. The extended emission in \ha,
	supports this interpretation. This burst is not apart of the statistical sample.

@@

	\subsection{GRB120404A (z = 2.876)}
	The data presented here has formed the basis of GCN \#
	13227\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13227.gcn3}}, but is not published otherwise. 9.6 ks integration, starting 15.7 hours after the \textit{Swift}-trigger reveals a low-intensity afterglow continuum on which absorption from \lya is detected in two distinct regions at redshifts $z=2.876$ and $z=.255$. These absorption systems are confirmed by ionic absorption features at both of these redshifts.

	\subsection{GRB120422A (z = 0.283)}
	The data presented here also formed the basis of GCN \#
	13257\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13257.gcn3}} and is published in \citet{Schulze2014}. A GRB-SN, this burst has been followed up multiple times. The data presented here only contain the first epoch in which the afterglow is still visible and before the rise of SN2012bz. Starting 16.5 hours after the burst, 4.8 ks integration time captures both the host and the burst in emission. A blue afterglow continuum is detected at all wavelengths covered by X-shooter, on which \mgii absorption at $z = 0.283$ is found. Offset by 1\farc75, the host is clearly detected at a consistent redshift with a rich emission line spectrum, the lines extending towards to burst.

	\subsection{GRB120712A (z = 4.175)}
	The data presented here also formed the basis of GCN \#
	13460\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13460.gcn3}} and is not
	published elsewhere. 4.8 ks integration time, starting 10.5 hours after the BAT trigger, shows a bright afterglow continuum starting at $\sim$ 4720 \AA, signifying the onset of the Lyman alpha forest, for a GRB located at $z = 4.175$. Absorption features from \lya, \feii, \mgii~and \SIii~are readily detected at a consistent redshift.
